GDM Workshop
========================================================

```{r}
gitpath<-"C:/Users/Jorge/Documents/GDMWorkshop/"
setwd(paste(gitpath,"Code_and_data",sep=""))

require(raster)
require(ecodist)
```

generate GDM input.r
---------------------
To add the environment values for each site pair

```{r fig.width=7, fig.height=6}
source("generate_site_pairs.r")
```

Add the environment values for each site pair
--------------------------------

This script takes a table with compositional dssimilarity between pairs of sites, and adds columns for environment at each of the sites, in the format required by GDM for Tables in R

```{r}
setwd(paste(gitpath,"Code_and_data/",sep=""))
source("generate_GDM_input.r")
```

Fit a GDM model
====================

> 1 the first section demonstrates how to prepare the data & run a single GDM;
> 2 the second section is the significance test function;
> 3 the third section explains and demonstrates the application of the significance test function.

```{r}
setwd(paste(gitpath,"Code_and_data/",sep=""))
source("gdm_fit_and_test.r")
```

